Model matters with restricted Boltzmann machines

### 2018-05-08 presentations/msmlc/slides.Rmd
msmlc

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 14, 2017
  |
  | Slides available at <http://bit.ly/kaplan-msu>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 14, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

\begin{figure}
\includegraphics[width=.55\linewidth]{../resources/images/toyhull_top.png}
\includegraphics[width=.35\linewidth]{../resources/images/toyhull_top_2.png}
\caption{The convex hull of the "statistic space" $\mathcal{T} = \{(v_1, h_1, v_1 h_1): v_1, h_1 \in \mathcal{C}\}$ in three dimensions for a toy RBM with one visible and one hidden node for $\mathcal{C} = \{0,1\}$ (left) and $\mathcal{C} = \{-1,1\}$ (right) data encoding.}
\end{figure}

The convex hull of $\mathcal{T} \subset \mathcal{C}^3$ does not fill the unit cube $[0,1]^3$ (left), but does better with $[-1,1]^3$ (right).

@@

- For the $\mathcal{C} = \{-1, 1 \}$ encoding of hiddens $(H_1, \dots, H_\nh)$ and visibles $(V_1, \dots, V_\nv)$, the origin is the center of the parameter space.
- At $\boldsymbol \theta = \boldsymbol 0$, RBM is equivalent to elements of $X$ being distributed as iid Bernoulli$\left(\frac{1}{2}\right)$ $\Rightarrow$ No *near-degeneracy*, *instability*, or *uninterpretability*!

@@

p
```

@@

* Slides -- <http://bit.ly/kaplan-msu>

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | May 9, 2017
  |
  | Slides available at <http://bit.ly/kaplan-msmlc>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "May 9, 2017"
output: 
  beamer_presentation:
    template: ../resources/latex/beamer.tex
    includes:
      in_header: ../resources/latex/front-matter.tex
theme: CambridgeUS
bibliography: ../resources/latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

\vspace{-.1in}
\begin{figure}
\includegraphics[width=.55\linewidth]{../resources/images/toyhull_top.png}
\includegraphics[width=.35\linewidth]{../resources/images/toyhull_top_2.png}
\caption{Convex hull of the "statistic space" $\mathcal{T} = \{(v_1, h_1, v_1 h_1): v_1, h_1 \in \mathcal{C}\}$ for a toy RBM with one visible and one hidden node for $\mathcal{C} = \{0,1\}$ (left) and $\mathcal{C} = \{-1,1\}$ (right) data encoding.}
\end{figure}
\vspace{-.15in}
- For the $\mathcal{C} = \{-1, 1 \}$ encoding of hiddens $(H_1, \dots, H_\nh)$ and visibles $(V_1, \dots, V_\nv)$, the origin is the center of the parameter space.
- At $\boldsymbol \theta = \boldsymbol 0$, RBM is equivalent to elements of $X$ being distributed as iid Bernoulli$\left(\frac{1}{2}\right)$ $\Rightarrow$ No *near-degeneracy*, *instability*, or *uninterpretability*!

<!--
The convex hull of $\mathcal{T} \subset \mathcal{C}^3$ does not fill the unit cube $[0,1]^3$ (left), but does better with $[-1,1]^3$ (right).

@@

@@

p
```
-->

@@

* Slides -- <http://bit.ly/kaplan-msmlc>
